---
title: "Lab 6"
author: "Varun Tanna"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

**Exercises:**  4 (Pg. 302); 1 (Pgs. 316-317); 1 (Pgs. 328-329); 1, 2 (Pgs. 353-354)

**Submission:** Submit via an electronic document on Sakai. Must be submitted as a HTML file generated in RStudio. All assigned problems are chosen according to the textbook *R for Data Science*. You do not need R code to answer every question. If you answer without using R code, delete the code chunk. If the question requires R code, make sure you display R code. If the question requires a figure, make sure you display a figure. A lot of the questions can be answered in written response, but require R code and/or figures for understanding and explaining.

```{r, include=FALSE}
library(tidyverse)
```

# Chapter 16 (Pg. 302)

##  Exercise 4

### a)
```{r}
library(modelr)

hold <- c(3,4,8,9)
fun1 <- function(x) {
  return(x[length(x)])
}

fun1(hold)
```

### b)
```{r}
fun2 <- function(x){
  
  return(x[seq(2, length(x), by = 2)])
}
fun2(hold)
```

### c)
```{r}
fun3 <- function(x){
  
  end <- length(x)-1
  
  return(x[1:end])
  
}

fun3(hold)
```

### d)
```{r}
fun4 <- function(x){
  indices <- which(x %% 2 ==0) 
return( x[indices])

}

fun4(hold)
```

# Chapter 17 (Pgs. 316-317)

##  Exercise 1

### a)
```{r}
temp <- data.frame(averages = c(0))

for(i in 1:ncol(mtcars)){
  
  temp1 <- mean(mtcars[,i])
  
  temp <- rbind(temp, temp1)
}
temp 
```

### b)
```{r}
temp <- data.frame(type = c(0))
library(tidyverse)
library(Stat2Data)
library(nycflights13)
data <- as.data.frame(nycflights13::flights)


for(i in 1:c(ncol(data))){
  type = class(data[,i])
  temp[i, 'type'] <- type[1]
  }

temp
```

### c)
```{r}
temp <- data.frame(numberunique = c(0))
library(tidyverse)
library(Stat2Data)
library(nycflights13)


for(i in 1:c(ncol(iris))){
  temp[i, 'numberunique'] <- length(unique(iris[,i]))
  }

temp
```

### d)
```{r}
list = c(-10, 0, 10, 100)

temp <- data.frame(first = c(0), second = c(0), third = c(0), fourth = c(0))

for(i in 1:length(list)){
  
  nums <- rnorm(10, mean = list[i], sd = 1)
  temp[1:10, i] <- nums
}

temp
```

# Chapter 17 (Pgs. 328-329)

##  Exercise 1

### a)
```{r}
apply(mtcars,   2, FUN = mean)
```

### b)
```{r}
library(nycflights13)
flights <- nycflights13::flights
apply(flights, 2, FUN = class)
```

### c)
```{r}
func1 <- function(x){
  
  return(length(unique(x)))
}

apply(iris, 2, FUN = func1)
```

### d)
```{r}
func2 <- function(x){
  
  return(rnorm(10, mean = x, sd = 1))
}


sapply(list,  FUN = func2)
```

# Chapter 18 (Pgs. 353-354)

##  Exercise 1
```{r}
tibs <- tibble(
  x = rep(1:10, each = 3), 
  y = x*1.5 + 6 + rt(length(x), df = 2)
  
)

  fit <- lm(y ~ x, tibs)
  summary(fit)
```
```{r}
plot(x = tibs$x, y = tibs$y)
```
model looks pretty linear and appropriate
##  Exercise 2
```{r}
make_prediction <- function(a, data){
  
  a[1] + data$x*a[2]
}

measure_distance <- function(mod, data){

  diff <- data$y - make_prediction(mod, data)
  mean(abs(diff))
}


optim(c(0,0), measure_distance, data = tibs)
```
different paremeters