---
title: "Lab 7"
author: "Varun Tanna"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Instructions

**Exercises:**  1,4 (Pg. 358); 1,4 (Pgs. 371)

**Submission:** Submit via an electronic document on Sakai. Must be submitted as a HTML file generated in RStudio. All assigned problems are chosen according to the textbook *R for Data Science*. You do not need R code to answer every question. If you answer without using R code, delete the code chunk. If the question requires R code, make sure you display R code. If the question requires a figure, make sure you display a figure. A lot of the questions can be answered in written response, but require R code and/or figures for understanding and explaining.

```{r, include=FALSE}
library(tidyverse)
library(modelr)
```


# Chapter 18 (Pg. 358)

##  Exercise 1
```{r}
sim1_loess <- loess(y ~ x, data = sim1)

grid_loess <- sim1 %>%
  add_predictions(sim1_loess)
sim1 <-  sim1 %>%
  add_residuals(sim1_loess, var = "resid_loess") %>%
  add_predictions(sim1_loess, var = "pred_loess")
plot_sim1_loess <- 
  ggplot(sim1, aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(x = x, y = pred), data = grid_loess, colour = "red")
plot_sim1_loess


ggplot(sim1, aes(x = x, y = y)) +
  geom_point() +
  geom_smooth(aes(x = x, y = pred), data = grid_loess, colour = "red")
```

##  Exercise 4
```{r}

#Showing the absolute values of the residuals makes it easier to view the spread of the residuals.
#The model assumes that the residuals have mean zero, and using the absolute values of the residuals #effectively doubles the number of residuals
```

# Chapter 18 (Pg. 371)

##  Exercise 1
```{r}
mod2a <- lm(y ~ x - 1, data = sim2)
mod2 <- lm(y ~ x, data = sim2)
grid <- sim2 %>%
  data_grid(x) %>%
  spread_predictions(mod2, mod2a)
grid
```
The predictions with and without the intercepts are the same
##  Exercise 4
```{r}
mod1 <- lm(y ~ x1 + x2, data = sim4)
mod2 <- lm(y ~ x1 * x2, data = sim4)
sim4_mods <- gather_residuals(sim4, mod1, mod2)
ggplot(sim4_mods, aes(x = resid, colour = model)) +
  geom_freqpoly(binwidth = 0.5) +
  geom_rug()
ggplot(sim4_mods, aes(x = abs(resid), colour = model)) +
  geom_freqpoly(binwidth = 0.5) +
  geom_rug()

```
The residual of mod2 are less spread out but there isn't really much difference in the model.